---
output:
  md_document:
    variant: markdown_github
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# badger: Badge for R Package

```{r, echo = FALSE, results='asis'}
cat(
	badge_cran_release("badger", "green"),
	badge_cran_download("badger", "grand-total", "green"),
	badge_cran_download("badger", "last-month", "green"),
	badge_cran_download("badger", "last-week", "green")
)
```

Query information and generate badge for using in README and GitHub Pages.

## Author

Guangchuang YU <https://guangchuangyu.github.io>

School of Basic Medical Sciences, Southern Medical University

[![saythanks](https://img.shields.io/badge/say-thanks-ff69b4.svg)](https://saythanks.io/to/GuangchuangYu)
`r badger::badge_custom("follow me on", "微信", "green", "https://guangchuangyu.github.io/blog_images/biobabble.jpg")`
`r badger::badge_custom("打赏", "支付宝/微信", "green", "https://guangchuangyu.github.io/blog_images/pay_qrcode.png")`


## Installation

Get the released version from CRAN:

```r
install.packages("badger")
```

Or the development version from github:

```r
## install.packages("devtools")
devtools::install_github("GuangchuangYu/badger")
```

----

## Examples

### Package Version

+ release version (bioconductor)
	- syntax: `` ``r ''`r badge_bioc_release("ggtree", "green")` ``
	- badge: `r badge_bioc_release("ggtree", "green")`
+ release version (CRAN)
	- syntax: `` ``r ''`r badge_cran("badger", "orange")` ``
	- badge: `r badge_cran_release("badger", "orange")` 
+ devel version
	- syntax: `` ``r ''`r badge_devel("guangchuangyu/ggtree", "blue")` ``
	- badge: `r badge_devel("guangchuangyu/ggtree", "blue")`

### Download stats for bioconductor

+ Total of total :)
	- syntax: `` ``r ''`r badge_bioc_download("clusterProfiler", "total", "blue",
    "total")` ``
	- badge: `r badge_bioc_download("clusterProfiler", "total", "blue",
    "total")`
+ Total of distinct IPs
	- syntax: `` ``r ''`r badge_bioc_download("clusterProfiler", "total", "yellow")` ``
	- badge: `r badge_bioc_download("clusterProfiler", "total", "yellow")`
+ Monthly download of distinct IPs
	- syntax: `` ``r ''`r badge_bioc_download("clusterProfiler", "month", "green")` ``
	- badge: `r badge_bioc_download("clusterProfiler", "month", "green")`
	
### Download stats for CRAN
	
+ Total downloads
	- syntax: `` ``r ''`r badge_cran_download("badger", "grand-total", "blue")` ``
	- badge: `r badge_cran_download("badger", "grand-total", "blue")`
+ Monthly Downloads
	- syntax: `` ``r ''`r badge_cran_download("badger", "last-month", "green")` ``
	- badge: `r badge_cran_download("badger", "last-month", "green")`
+ Weekly Downloads
	- syntax: `` ``r ''`r badge_cran_download("badger", "last-week", "yellow")` ``
	- badge: `r badge_cran_download("badger", "last-week", "yellow")`


### Impact

+ Altmetric score
	- syntax: `` ``r ''`r badge_altmetric("10533079", "green")` ``
	- badge: `r badge_altmetric("10533079", "green")`


### Academic

+ DOI
	- syntax: `` ``r ''`r badge_doi("10.1111/2041-210X.12628", "yellow")` ``
	- badge: `r badge_doi("10.1111/2041-210X.12628", "yellow")`

### Customize badge

+ syntax: `` ``r ''`r badge_custom("1st most cited paper", "in OMICS", "blue",
  "http://online.liebertpub.com/action/showMostCitedArticles?journalCode=omi")` ``
+ badge: `r badge_custom("1st most cited paper", "in OMICS", "blue",
  "http://online.liebertpub.com/action/showMostCitedArticles?journalCode=omi")`
  
### Development

+ Lifecycle
	- syntax: `` ``r ''`r badge_lifecycle("maturing", "blue")` ``
	- badge: `r badge_lifecycle("maturing", "blue")`
+ travis build-status
	- syntax: `` ``r ''`r badge_travis("rstudio/rmarkdown")` ``
	- badge: `r badge_travis("rstudio/rmarkdown")`
+ coveralls code coverage
	- syntax: `` ``r ''`r badge_coveralls("google/benchmark")` ``
	- badge: `r badge_coveralls("google/benchmark")`
+ code size
	- syntax: `` ``r ''`r badge_code_size("GuangchuangYu/badger")` ``
	- badge: `r badge_code_size("GuangchuangYu/badger")`
+ last commit date
	- syntax: `` ``r ''`r badge_last_commit("GuangchuangYu/badger")` ``
	- badge: `r badge_last_commit("GuangchuangYu/badger")`
+ direct and recursive dependencies (for CRAN pkgs)
	- syntax: `` ``r ''`r badge_dependencies("badger")` ``
	- badge: `r badge_dependencies("badger")`